\documentclass[
11pt,%
tightenlines,%
twoside,%
onecolumn,%
nofloats,%
nobibnotes,%
nofootinbib,%
superscriptaddress,%
noshowpacs,%
centertags]%
{revtex4}
\usepackage{ljm}
\usepackage{listings}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}

\lstset{
language=C++,
basewidth=0.5em,
xleftmargin=45pt,
xrightmargin=45pt,
basicstyle=\small\ttfamily,
keywordstyle=\bfseries\underbar,
numbers=left,
numberstyle=\tiny,
stepnumber=1,
numbersep=10pt,
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=trBL,
tabsize=2,
captionpos=t,
breaklines=true,
breakatwhitespace=false,
escapeinside={\%*}{*)}
}

\begin{document}

\titlerunning{Computational mesh evolution}
\authorrunning{Meshcheryakov et al.}

\title{Evolution of the surface computational mesh in the ice accretion process}

\author{\firstname{A.~O.}~\surname{Meshcheryakov}}
\email[E-mail: ]{alex2501@jscc.ru}
\affiliation{Joint Supercomputer Center of the Russian Academy of Sciences -- branch of Scientific Research Institute of System Analysis of the Russian Academy of Sciences, Leninsky prospect 32a, Moscow, 119334, Russia}

\author{\firstname{A.~A.}~\surname{Rybakov}}
\email[E-mail: ]{rybakov@jscc.ru}
\affiliation{Joint Supercomputer Center of the Russian Academy of Sciences -- branch of Scientific Research Institute of System Analysis of the Russian Academy of Sciences, Leninsky prospect 32a, Moscow, 119334, Russia}

\firstcollaboration{(Submitted by TODO)} % Add if you know submitter.
%\lastcollaboration{ }

\received{TODO}

\begin{abstract}
Задача моделирования обледенения поверхности обтекаемого тела является критической для обеспечения безопасности полетов в условия ледообразования.
Формирование ледяных наростов на несущих частях и элементах силовых установок летальных аппаратов может существенно влиять на летные характеристики.
Сам процесс ледообразования является комплексным.
Для получения качественной картины профиля ледяного нароста необходимо учитывать множество физических процессов, включая динамику газа, теплопроводность, динамику капель, выпадающих на поверхность, течение жидкости по поверхности.
Расчет ледяного покрова должен выполняться итерационно, так как образующийся лед существенно влияет на газодинамические характеристики, которые должны пересчитываться с ростом льда.
Важной частью моделирования является эволюция поверхности тела в процессе ледообразования.
В настоящей статье рассматриваются различные подходы к моделированию эволюции поверхности, предлагается новый алгоритм построения новой поверхности с помощью общей огибающей семейства сфер, центры которых находятся на исходной поверхности.
В процессе эволюции на поверхности могут образовываться различные артефакты и аномалии, из-за которых проведение дальнейших расчетов может стать невозможным.
Для устранения этих препятствий в статье рассматриваются методы адаптации расчетной сетки в процессе эволюции, а также устранения потенциальных самопересечений, препятствующих дальнейшим расчетам.
\end{abstract}

%\subclass{TODO subclass} % Enter 2010 Mathematics Subject Classification.

\keywords{Ледообразование, неструктурированная поверхностная расчетная сетка, эволюция поверхности.}

\maketitle

%---------------------------------------------------------------------------------------------------

\section{Introduction}
\input{introduction}

%---------------------------------------------------------------------------------------------------

\section{Mesh architecture}
\input{architecture}

%---------------------------------------------------------------------------------------------------

\section{Remeshing}
\input{remesh}
\subsection{Classical remeshing methods}
\input{remesh_classical}
\subsection{Перестроение сохранением объема}
\input{remesh_tong}
\subsection{Метод общей огибающей}
\input{remesh_envelope}

%---------------------------------------------------------------------------------------------------

\section{Adaptation}
\input{adaptation}

%---------------------------------------------------------------------------------------------------

\section{Устранение самопересечений}
\input{sle}

%---------------------------------------------------------------------------------------------------

\section{Conclusion}
\input{conclusion}

\begin{acknowledgments}
The work was carried out at the JSCC RAS as part of the government assignment (topic FNEF-2022-0016). Supercomputer MVS-10P was used in research.
\end{acknowledgments}

%---------------------------------------------------------------------------------------------------

\begin{thebibliography}{99}

% Introduction.

\bibitem{Raj}
\refitem{article}
L.~Prince Raj, K.~Yee, and R.~S.~Myong, \textquotedblleft Sensivity of ice and aerodynamic performance degradation to critical physical and modeling parameters affecting airfoil icing,\textquotedblright \ Aerospace Science and Technology, {\bf 98}, 105659 (2020).

\bibitem{Martini}
\refitem{article}
F.~Martini, H.~Ibrahim, L.~T.~C.~Montoya, P.~Rizk, and A.~Ilinca, \textquotedblleft Turbulence modeling of iced wind turbine airfoils,\textquotedblright \ Energies, {\bf 15}, 8325 (2022).

\bibitem{Strijhak}
\refitem{article}
S.~Strijhak, V.~Melnikova, and K.~Koshelev, \textquotedblleft Development of iceFoam solver for modeling ice accretion,\textquotedblright \ in \textit{Proceedings of the Institute for System Programming of RAS, 2020}.

\bibitem{Sorokin}
\refitem{article}
K.~E.~Sorokin, P.~M.~Byvaltsev, A.~A.~Aksenov, S.~V.~Zhluktov, D.~V.~Savitskiy, A.~A.~Babulin, and V.~I.~Shevyakov, \textquotedblleft Numerical simulation of ice accretion if FlowVision sotfware,\textquotedblright \ Computer Research and Modeling, {\bf 12}, №~1, 83--96 (2020).

\bibitem{Galanov}
\refitem{article}
N.~G.~Galanov, A.~V.~Sarazov, R.~N.~Zhukov, and A.~S.~Kozelkov, \textquotedblleft Application of various ice accretion simulation approaches in the LOGOS software package,\textquotedblright \ Journal of Physics: Conference Series, {\bf 2099}, 012029 (2021).

\bibitem{Bartkus}
T.~P.~Bartkus, P.~M.~Struk, and J.-C.~Tsao, \textquotedblleft Evaluation of a thermodynamic ice-crystal icing model using experimental ice accretion data,\textquotedblright \ in \textit{Proceedings of the Atmospheric and Space Environments Conference, 2018}

\bibitem{Zhang}
X.~Zhang, X.~Wu, and J.~Min, \textquotedblleft Aircraft icing model considering both rime ice property variability and runback water effect,\textquotedblright \ International Journal of Heat and Mass Transfer, {\bf 104}, 510--516 (2017).

\bibitem{Pena}
D.~Pena, Y.~Hoarau, and E.~Laurendeau, \textquotedblleft A single step ice accretion model using level-set method,\textquotedblright \ Journal of Fluids and Structures, {\bf 65}, 278--294 (2016).


% Remesh.

\bibitem{Beaugendre}
\refitem{misc}
H.~Beaugendre, \textquotedblleft A PDE-based approach to in-flight ice accretion,\textquotedblright \ PhD Thesis (Dep. of Mech. Eng., McGill Univ., Montr\'eal, Qu\'ebec, 2003).

\bibitem{Rybakov_2D}
\refitem{article}
A.~Rybakov and S.~Shumilin, \textquotedblleft Approximate methods of the surface mesh deformation in two-dimensional case,\textquotedblright \ Lobachevskii J Math {\bf 40}, 1848--1852 (2019).

\bibitem{BourgaultCote}
\refitem{article}
S.~Bourgault-C\^ot\'e, K.~Hasanzadeh, P.~Lavoie, and E.~Laurendeau, \textquotedblleft Multi-layer icing methodologies for conservative ice growth,\textquotedblright \ in \textit{Proceedings of 7th European Conference for Aeronautics and Aerospace Sciences EUCASS, 2017}.

\bibitem{Thompson}
\refitem{article}
D.~Thompson, X.~Tong, Q.~Arnoldus, E.~Collins, D.~McLaurin, and E.~Luke, \textquotedblleft Discrete surface evolution and mesh deformation for aircraft icing applications,\textquotedblright \ in \textit{Proceedings of the 5th AIAA Atmospheric and Space Environments Conference, 2013}.

\bibitem{Tong}
\refitem{article}
X.~Tong, D.~Thompson, Q.~Arnoldus, E.~Collins, and E.~Luke, \textquotedblleft Three-dimensional surface evolution and mesh deformation for aircraft icing applications,\textquotedblright \ Journal of Aircraft, {\bf 54}, 1047--1063 (2017).

\bibitem{Jiao}
\refitem{article}
X.~Jiao, \textquotedblleft Face offsetting: a unified approach for explicit moving interfaces,\textquotedblright \ Journal of Computational Physiscs, {\bf 220}, 612--625 (2007).

\bibitem{Jiao_null_space_smooth}
\refitem{article}
X.~Jiao, \textquotedblleft Volume and feature preservation in surface mesh optimization,\textquotedblright \ in \textit{Proceedings of the 15th International Meshing Roundtable, 2006}.

% Adaptation.

\bibitem{Rivara}
\refitem{article}
M.-C.~Rivara and P.~A.~Rodrigez-Moreno, \textquotedblleft Tuned terminal triangles centroid Delaunay algorithm for quality triangulation,\textquotedblright \ in \textit{27th International Meshing Roundtable, 2019}.

\bibitem{Rakotoarivelo}
\refitem{article}
H.~Rakotoarivelo and F.~Ledoux, \textquotedblleft Accurate manycore-accelerated manifold surface remesh kernels,\textquotedblright \ in \textit{27th International Meshing Roundtable, 2019}.

\bibitem{Borouchaki}
\refitem{article}
H.~Borouchaki, P.~Laug, and P.-L.~George, \textquotedblleft Parametric surface meshing using a combined advancing-front generalized Delaunay approach,\textquotedblright \ International Journal for Numerical Methods in Engineering, {\bf 49}, 233--259 (2000).

\bibitem{Panchal}
\refitem{article}
D.~Panchal and D.~Jayaswal, \textquotedblleft Feature sensitive geometrically faithful highly regular direct triangular isotropic surface remeshing,\textquotedblright \ S$\bar{a}$dhan$\bar{a}$, {\bf 47}, 94 (2022).

% SLE

\bibitem{Jung}
\refitem{article}
W.~Jung, H.~Shin, and B.~K.~Choi, \textquotedblleft Self-intersection removal in triangular mesh offsettings,\textquotedblright \ CAD Journal, {\bf 1}, № 1, 477--484 (2004).

\bibitem{Freylekhman}
\refitem{article}
S.~A.~Freylekhman and A.~A.~Rybakov, \textquotedblleft Self-intersection elimination for unstructured surface computational meshes,\textquotedblright \ Lobachevskii J Math {\bf 43}, 134--140 (2022).

\bibitem{Charton}
\refitem{article}
J.~Charton, S.~Baek, and Y.~Kim, \textquotedblleft Mesh repairing using topology graphs,\textquotedblright \ Journal of Computational Design and Engineering, {\bf 8}, 251--267 (2021).

\bibitem{Skvorkovska}
\refitem{article}
V.~Skorkovsk\'a, I.~Kolingerov\'a, and B.~Benes, \textquotedblleft A Simple and robust approach to computation of meshes intersection,\textquotedblright \ in \textit{Proceedings of the 13th International Joint Conference on Computer Vision, Imaging and Computer Graphics Theory and Applications, {\bf 1}, 175--182, 2018}.

\end{thebibliography}

\end{document}
