%%
%% ****** ljmsamp.tex 13.06.2018 ******
%%
\documentclass[
11pt,%
tightenlines,%
twoside,%
onecolumn,%
nofloats,%
nobibnotes,%
nofootinbib,%
superscriptaddress,%
noshowpacs,%
centertags]%
{revtex4}
\usepackage{ljm}
\usepackage{listings}
\usepackage{amsmath,amsthm,amscd,amsfonts,amssymb}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{esvect}
\usepackage{physics}

\lstset{
language=C++,
basewidth=0.5em,
xleftmargin=45pt,
xrightmargin=45pt,
basicstyle=\small\ttfamily,
keywordstyle=\bfseries\underbar,
numbers=left,
numberstyle=\tiny,
stepnumber=1,
numbersep=10pt,
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=trBL,
tabsize=2,
captionpos=t,
breaklines=true,
breakatwhitespace=false,
escapeinside={\%*}{*)}
}

\begin{document}

\titlerunning{Dynamic objects type identification algorithm robustness} % for running heads
\authorrunning{A.~N.~Katulev, A.~N.~Sotnikov, V.~K.~Kemaikin, I.~V.~Kozhukhin} % for running heads
%\authorrunning{First-Author, Second-Author} % for running heads

\title{Robustness of the algorithm of identification of the type of dynamic object found at the finite sequence of 2D background frames of the optoelectron device}

% Splitting into lines is performed by the command \\
% The title is written in accordance with the rules of capitalization.

\author{\firstname{A.~N.}~\surname{Katulev}}
\email[E-mail: ]{katuleva@mail.ru}
\affiliation{Central Research Institute of Aerospace Defense Forces of Ministry of Defense of the Russian Federation, Afanasiy Nikitin Embankment, building 32, Tver, 170026, Russia}

\author{\firstname{A.~N.}~\surname{Sotnikov}}
\email[E-mail: ]{asotnikov@jscc.ru}
\affiliation{Joint Supercomputer Center of the Russian Academy of Sciences - branch of Scientific Research Institute of System Analysis of the Russian Academy of Sciences, Leninsky prospect 32a, Moscow, 119334, Russia}

\author{\firstname{V.~K.}~\surname{Kemaikin}}
\email[E-mail: ]{vk-kem@mail.ru}
\affiliation{State Technical University, Lenin Avenue, building 25, Tver, 170023, Russia}

\author{\firstname{I.~V.}~\surname{Kozhukhin}}
\email[E-mail: ]{kozhukhin@mail.ru}
\affiliation{State Technical University, Lenin Avenue, building 25, Tver, 170023, Russia}

%\noaffiliation % If the author does not specify a place of work.

\firstcollaboration{(Submitted by TODO : SUBMITTER)} % Add if you know submitter.
%\lastcollaboration{ }

\received{TODO : DATE} % The date of receipt to the editor, i.e. December 06, 2017

\begin{abstract}
Here are proposed robustness characteristics of the algorithm of identification of the type of the dynamic object (DO) and the law of probability distribution of identification sufficient statistics, formed by the algorithm under prior uncertainty.
The law is applied for verification and validation of the algorithm.
Wavelet fractal correlation algorithm (WFCA) implements vectorial criterion of ratio of likelihood functions of simple alternative hypotheses - types of DOs, this criterion being invariant to specific features of DO motion trajectories.
The likelihood functions are reconstructed by simulation according to sufficiently representative complexes of implementations of fractal dimensions, energies, wavelet spectra and maximum eigenvalues of biased correlation matrices as functional of the measured coordinates of spatial attitude of various types of real DOs located by the optoelectron device (OED).
The simulation proved  robustness and high efficiency of the algorithm of identification of the type of DOs.
\end{abstract}

%\subclass{TODO : CODE} % Enter 2010 Mathematics Subject Classification.

\keywords{identification algorithm, dynamical object, optoelectronic device} % Include keywords separeted by comma.

\maketitle

% Text of article starts here.

\section{Relevance}

\input{relevance}

\section{The objective of article}

\input{objective}

\section{Wavelet-fractal-correlation algorithm: the structure and properties}

\input{wave_frac_cor_algorithm}

\section{The stability of the initial sufficient statistics for the DO type identification algorithm}

\input{stability_1}

\section{The stability of the recognition algorithm type}

\input{stability_2}

\section{The probability distribution law of statistics recognition of DO type. Stability properties.}

\input{probability}

\section{Performance indicators of DO type identification algorithm}

\input{performance}

\section{Conclusion}

\input{conclusion}

\begin{thebibliography}{99}

\bibitem{bib_01}
\refitem{article}
A.~N.~Katulev, A.~A.~Khramichev, {\it ``A wavelet-fractal-correlation algorithm for recognizing the type of a dynamic object detected on a finite sequence of 2D phonon-image frames of an optoelectronic device"}, Optical Journal, T.~84, 1--10 (2017).

\bibitem{bib_02}
\refitem{book}
A.~A.~Potapov, Yu.~V.~Gulyaev, S.~A.~Nikitov, A.~A.~Pakhomov, V.~A.~German, {\it ``The newest methods of image processing"}, Moscow: Fizmatlit, 496 p. (2008).

\bibitem{bib_03}
\refitem{book}
V.~A.~Ponkin, E.~V.~Peteshchenkov, E.~M.~Afanasyeva, {\it ``Optical visibility of aircraft"}, Voronezh: "The Scientific Book", 553 p. (2015).

\bibitem{bib_04}
\refitem{book}
B.~A.~Alpatov, P.~V.~Babayan, O.~E.~Balashov, A.~I.~Stepashkin, {\it ``Methods of automatic detection and tracking of objects. Image processing and management"}, Moscow: Radio Engineering, 176 p. (2008).

\bibitem{bib_05}
\refitem{article}
Autometry, T.~50, No.~1--6 (2014); T.~51, No.~1--6 (2015); T.~52, No.~1--5 (2016).

\bibitem{bib_06}
\refitem{article}
Computeroptics, T.~37, 38, 39, 40 (2013--2016).

\bibitem{bib_07}
\refitem{book}
G.~I.~Ivchenko, Yu.~I.~Medvedev, {\it ``Math statistics"}, Moscow: VSh, 248 p. (1984).

\bibitem{bib_08}
\refitem{book}
{\it ``Directory of the officer of aerospace defense"}, Tver, 564 p. (2008).

\bibitem{bib_09}
\refitem{book}
D.~Cox, D.~Hinckley, {\it ``Theoretical statistics"}, Moscow: Mir, 560 p. (1978).

\bibitem{bib_10}
\refitem{article}
S.~Wilks, {\it ``Mathematical statistics"}, Moscow: Nauka, 632 p. (1967).

\bibitem{bib_11}
\refitem{book}
P.~Huber, {\it ``Robustness in statistics"}, Moscow: Mir, 304 p. (1984).

\bibitem{bib_12}
\refitem{book}
A.~K.~Mitropolsky, {\it ``The technique of statistical computations"}, Moscow: Nauka, 576 p. (1971).

\bibitem{bib_13}
\refitem{book}
G.~Kramer, {\it ``Mathematical methods of statistics"}, M.: The World, 648 p. (1975).

\bibitem{bib_14}
\refitem{book}
N.~V.~Smirnov, I.~V.~Dunin-Barkovsky, {\it ``A short course of mathematical statistics for technical applications"}, Moscow: FML, 436 p. (1959).

\bibitem{bib_15}
\refitem{book}
N.~A.~Livshits, V.~N.~Pugachev, {\it ``Probabilistic analysis of automatic control systems"}, Moscow: Sov. Radio, 896 p. (1963).

\bibitem{bib_16}
\refitem{book}
S.~A.~Aivazyan, I.~S.~Enyukov, L.~D.~Meshalkin, {\it ``Applied statistics, Т.~1, Fundamentals of modeling and primary data processing"},  Moscow: Finances and Statistics, 471 p. (1983).

\bibitem{bib_17}
\refitem{book}
A.~N.~Kolmogorov, S.~V.~Fomin, {\it ``Elements of the theory of functions and functional analysis"}, M.: Science, 406 p. (1968).

\bibitem{bib_18}
\refitem{book}
V.~S.~Korolyuk, N.~I.~Portenko, A.~V.~Skorokhod, A.~F.~Turbin, {\it ``A handbook on probability theory and mathematical statistics"}, Moscow: Nauka, 640 p. (1985).

\bibitem{bib_19}
\refitem{book}
Yu.~V.~Prokhorov, Yu.~A.~Rozanov, {\it ``Probability theory. Basic concepts. Limit theorems. Random processes"}, Moscow: Nauka, 406 p. (1967).

\bibitem{bib_20}
\refitem{book}
A.~E.~Basharinov, B.~S.~Fleishman, {\it ``Methods of statistical sequential analysis and their radio engineering applications"}, Moscow: Sov. Radio, 352 p. (1962).

\bibitem{bib_21}
\refitem{book}
S.~Z.~Kuzmin, {\it ``Fundamentals of the theory of digital processing of radar information"}, Moscow: Sov. Radio, 432 p. (1974).

\bibitem{bib_22}
\refitem{book}
V.~A.~Malyshev, I.~M.~Khmarov, O.~V.~Malyshev etc., {\it ``Recognition of surface objects and aircrafts by 2D and 3D optoelectronic systems"}, Moscow: FGUP NTC Informatika, 158 p. (2013).

\end{thebibliography}

\end{document}
